`SimSurvey`: an `R` package for simulation testing the design and analysis of fisheries-independent trawl surveys

### 2019-07-04 analysis/paper/sim_survey_paper.Rmd
Address the remainder of Greg's comments (except suggestion for new plot that compares real and simulated survey data; work on that next)

TODO:
> in each section, expand upon the details of the core functions and the associated equation symbols (i.e. break down case-study table into several tables)
> in the case study section, copy and paste (and clean-up) the code used to generate the case study results

@@

Table: (\#tab:abundance) Default `sim_abundance` function call, with argument descriptions and associated parameter symbols.

| **Function call**                           | **Description**                                            | **Symbol**                 |
|:------------------------------------------- |:---------------------------------------------------------- | :------------------------- |
| `sim_abundance(`                            | &nbsp;                                                     | &nbsp;                     |
| `+  ages = 1:20,`                           | Ages                                                       | $a$                        |
| `+  years = 1:20,`                          | Years                                                      | $y$                        |
| `+  R = sim_R(mean = 30000000,`             | Mean recruitment                                           | $\mu_r$                    |
| `+            log_sd = 0.5),`               | Standard deviation of log-recruitment                      | $\sigma_r$                 |
| `+  Z = sim_Z(mean = 0.5,`                  | Mean total mortality                                       | $\mu_Z$                    |
| `+            log_sd = 0.2,`                | Standard deviation of total mortality                      | $\sigma_Z$                 |
| `+            phi_age = 0.9,`               | Correlation across ages in error around total mortality    | $\varphi_{\delta, age}$    |
| `+            phi_year = 0.5),`             | Correlation across years in error around total mortality   | $\varphi_{\delta, year}$   |
| `+  growth = sim_vonB(Linf = 120,`          | Mean asymptotic length (cm)                                | $l_{\infty}$               |
| `+                    L0 = 5,`              | Length at birth (cm)                                       | $l_0$                      |
| `+                    K = 0.1,`             | Growth rate                                                | $K$                        |
| `+                    log_sd = 0.1,`        | Standard deviation of the von Bertalanffy growth curve     | $\sigma_l$                 |
| `+                    length_group = 3))`   | Length group for abundance at length (cm)                  | $l_{group}^{N}$            |

@@

Abundance is simulated using the `sim_abundance` function and a default function call is described in Table \@ref(tab:abundance). This function has a simple structure and requires the specification of a series of `ages` and `years` along with functions for simulating recruitment (`R`), total mortality (`Z`) and growth (`growth`). The package includes the functions `sim_R`, `sim_Z` and `sim_vonB` for simulating recruitment, total mortality and growth, respectively. These functions are "closures" [i.e. functions that contain data and return functions; @wickham2014] and this structure was chosen to avoid the repeated specifications of ages and years. The use of closures also allows users to use their own closures with a similar structure but different underlying formula. Overall, the function provides a simple tool for simulating a range dynamic age-structured populations. For instance, below we simulate a relatively long (default case study settings) and short lived species.

@@

The package also includes several plotting function for making quick plotly-based [@sievert2018] interactive visuals of the simulated population. For instance, the `plot_surface` function can be used to make quick visuals of matrices contained within the list returned by `sim_abundance`. The plots output from the below code are combined into Figure \@ref(fig:surface). Here we display the abundance at age matrix (object named `N` in the list produced by `sim_abundance`); other names can be supplied to the `mat` argument to visualize a different matrix from the `sim_abundance` list, such as `Z`.

@@

```{r surface, fig.cap = "Surface plots of simulated abundance at age of a relatively a) long lived (case study settings) and b) short lived species. These plots were produced by `plot_surface` when supplied a list produced by `sim_abundance`."}

@@

The next step in the simulation is to distribute the abundance at age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ locations was generated with a resolution of $R$ and a depth gradient. The depth gradient was set-up to have a sigmoid shape with a depth range of $[d_{min}, d_{max}]$, shelf depth of $d_{shelf}$ and a shelf width of $w_{shelf}$. The grid is divided into $N_{div}$ divisions and $N_{strat}$ depth-based strata. The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean. This helps simulate depth preferences of particular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation, and the age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations was controlled by a smoothing ($\lambda$) and scaling parameter ($\kappa$) [here we approximate $\kappa$ from a range parameter ($r$), $\kappa = \sqrt{8 \lambda} / r$; @Blangiardo2015] and correlation across ages and years was controlled by $\varphi_{\xi, age}$ and $\varphi_{\xi, year}$, respectively. The overall variance of the process was controlled by $\sigma_{\xi}^2$. In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid. A more detailed description of the space-age-year covariance is included in Appendix 2. Note that the the distributions of specific length groups were not simulated because of the greater computational cost of storing spatially dis-aggregated abundance across all length groups.

Table: (\#tab:distribution) Default `sim_distribution` function call, with argument descriptions and associated parameter symbols.

| **Function call**                                       | **Description**                                       | **Symbol**            |
|:------------------------------------------------------- |:----------------------------------------------------- | :-------------------- |
| `sim_distribution(`                                     | &nbsp;                                                | &nbsp;                |
| `+  sim,`                                               | Simulated population from `sim_abundance`             | &nbsp;                |
| `+  grid = make_grid(x_range = c(-140, 140),`           | Range of grid in the x dimension                      | &nbsp;                |
| `+                   y_range = c(-140, 140),`           | Range of grid in the y dimension                      | &nbsp;                |
| `+                   res = c(3.5, 3.5),`                | Grid resolution (km)                                  | $R$                   |
| `+                   shelf_depth = 200,`                | Shelf depth (km)                                      | $d_{shelf}$           |
| `+                   shelf_width = 100,`                | Shelf width (km)                                      | $w_{shelf}$           |
| `+                   depth_range = c(0, 1000),`         | Depth range (m)                                       | $[d_{min}, d_{max}]$  |
| `+                   n_div = 1,`                        | Number of divisions                                   | $N_{div}$             |
| `+                   strat_breaks = seq(0, 1000, 40)),` | Series of depth breaks for defining strata            | &nbsp;                |
| `+  ays_covar = sim_ays_covar(sd = 2.8,`                | Standard deviation of age-year-space distribution     | $\sigma_{\xi}$        |
| `+                            range = 300,`             | Range of spatial correlation (km)                     | $r$                   |
| `+                            phi_age = 0.5,`           | Correlation across ages in spatial distribution       | $\varphi_{\xi, age}$  |
| `+                            phi_year = 0.9,`          | Correlation across years in spatial distribution      | $\varphi_{\xi, year}$ |
| `+                            group_ages = 5:20),`      | Make space-age-year variance equal across these ages  | &nbsp;                |
| `+  depth_par = sim_parabola(mu = 200,`                 | Depth at which abundance is typically highest (m)     | $\mu_d$               |
| `+                           sigma = 70))`              | Dispersion around depth of peak abundance (m)         | $\sigma_d$            |

@@

The `make_grid` function is used to generate a survey grid for use in the `sim_distribution` function. The output from `make_grid` is a raster object [@hijmans2016] with four layers: `depth`, `cell`, `division` and `strat`. If a more detailed and realistic grid is required, users can manually generate their own survey grid using real data and this grid can be supplied to `sim_distribution` if the same structure is used. The package includes a manually constructed survey grid of NAFO division 3Ps (named `survey_grid`) and the data-raw folder in the GitHub directory includes the data and code used to construct this grid. However, for simplicity, we use `make_grid` to construct a square grid for our case study and the settings used are shown in Table \@ref(tab:par). Below we generate and plot (combined in Figure \@ref(fig:grid)) a default case study grid and another grid with four divisions and a more linear gradient in depth.

@@

a <- make_grid(n_div = 1, shelf_depth = 200,
               shelf_width = 100, depth_range = c(0, 1000))
b <- make_grid(n_div = 4, shelf_depth = 500, 
               shelf_width = 0, depth_range = c(0, 1000))
plot_grid(a)
plot_grid(b)

@@

a <- make_grid() %>% 
  plot_grid(showscale = TRUE) %>% 
  add_labels(x = 0, y = 1, text = "a)")
b <- make_grid(n_div = 4, shelf_depth = 500, shelf_width = 0, depth_range = c(0, 1000)) %>% 
  plot_grid(showscale = FALSE) %>% 
  add_labels(x = 0.01, y = 1, text = "b)")
p <- subplot(a, b)

export_plot(p, file = "analysis/paper/figures/plot_grid.png", width = 800, height = 430)

@@

```{r grid, fig.cap = "Plots produced by `plot_grid` when supplied an raster object produced by `make_grid` a) using default case study settings and b) settings generates a grid with four divisions and a more linear depth gradient. In these plots, the color gradient represents depth, the grey lines delineate divisions and white lines delineate strata."}

@@

The `sim_distribution` function distributes the population simulated using `sim_abundance` throughout the grid generated using `make_grid`. Table \@ref(tab:distribution) outlines the default settings used for the function. In addition to supplying objects produced by `sim_abundance` and `make_grid`, this function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by tweaking a few parameters in these closures. Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider range) and exhibits stronger correlation across ages than years. Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years`, respectively, arguments in the `sim_ays_covar` closure. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fidelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the **`SimSurvey`** package have been set-up to be pipe [`%>%`; @bache2014] friendly.

@@

set.seed(438)
a <- sim_abundance() %>% 
  sim_distribution(ays_covar = sim_ays_covar(range = 300,
                                             phi_year = 0.9,
                                             phi_age = 0.5))
b <- sim_abundance() %>% 
  sim_distribution(ays_covar = sim_ays_covar(range = 2000,
                                             phi_year = 0.2,
                                             phi_age = 0.9))

@@

This function retains all the data simulated by `sim_abundance` and adds a data.table [@dowle2017], named `sp_N`, with abundance (`N`) split by `age`, `year` and `cell`. The function also retains the grid object and converts these data into a data.table, named `grid_xy`, with headers `x`, `y`, `depth`, `cell`, `division` and `strat`. The `sp_N` object can be merge with the `grid_xy` data by `cell` to associate abundance with specific locations, depth, divisions or strata. The `plot_distribution` function can be used to provide a quick visual of the distribution across ages and years. The code below will generate interactive plots with an Age-Year slider, however, for this paper we present a facet plot of the simulated data in Figure \@ref(fig:distribution).

@@

```{r distribution, fig.cap = "Distribution plots of simulated populations that form a) tight clusters with stronger correlation through years than ages (case study settings), and b) relatively diffuse clusters with stronger correlation through ages than years. This plot is a facet of plots produced by `plot_distribution` when supplied simulations from `sim_distribution`."}

@@

The final step in the simulation is to conduct a stratified random survey over the age-year-space array generated using formula described above. The area of each strata is calculated and this is used to define the sets to allocate to each strata under a particular set density, $D_{sets}$. The allocated number of cells are randomly selected in each strata and the number of fish caught in each set is calculated by applying binomial sampling of the fish in each sampled cell by the proportion of the area covered by the trawl and the catchability of each age:

$$n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A_{trawl}}{A_{cell}} q_a )$$
Where $n_{a,y,s}$ is the number of fish sampled by a set, $A_{trawl}$ indicates the area covered by the trawl, $A_{cell}$ is the area of a grid cell (i.e. $R^2$), and $q_a$ is the catchability coefficient of each age. Here, catchabilities were defined using a logistic curve controlled by a steepness, $k$, and midpoint parameter, $x_0$. The lengths of the fish sampled by the set are then simulated using the von Bertalanffy growth equation found above in the [Simulate abundance] section. Depending on the number of fish caught, sub-sampling is then conducted. Specifically, a maximum number of lengths are measured per set, $M_{lengths}$, and a maximum number of ages, $M_{ages}$, are sampled per length group, $l_{group}$, per division. Such sub-sampling is common in fisheries-independent surveys as it is costly to sample every fish sampled. Age determination is especially time-consuming, which is why age sampling tends to be length-stratified.

@@

| **Function call**                   | **Description**                                                         | **Symbol**     |
|:----------------------------------- |:----------------------------------------------------------------------- | :------------- |
| `sim_survey(`                       | &nbsp;                                                                  | &nbsp;         |
| `+  sim,`                           | Simulated spatial population from `sim_distribution`                    | &nbsp;         |
| `+  n_sims = 1`                     | Number of times to repeat the survey                                    | &nbsp;         |
| `+  q = sim_logistic(k = 2,`        | Steepness of logistic curve of catchability                             | $k$            |
| `+                   x0 = 3),`      | Midpoint of logistic curve of catchability                              | $x_0$          |
| `+  trawl_dim = c(1.5, 0.02),`      | Trawl dimensions (length, width; km) - i.e. area covered by a trawl     | $A_{trawl}$    |
| `+  min_sets = 2`                   | Minimum number of sets to conduct per strata                            | &nbsp;         |
| `+  set_den = 2/1000,`              | Set density (km^-2^)                                                    | $D_{sets}$     |
| `+  lengths_cap = 500,`             | Maximum number of lengths to collect / set                              | $M_{lengths}$  |
| `+  length_group = 1,`              | Length group for age sampling (cm)                                      | $l_{group}$    |
| `+  ages_cap = 10,`                 | Maximum number of ages to sample / length group / division              | $M_{ages}$     |
| `+  age_sammpling = "stratified")`  | Controls whether age sampling is length `"stratified"` or `"random"`    | &nbsp;         |

@@

The function `sim_survey` can be used to simulate data from one survey over a population simulated using `sim_distribution`. A default function call is described in Table \@ref(tab:survey)). This function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Multiple simulations of the same survey can be run using the `n_sims` argument, however, it is important not to request large numbers of simulations because this function can quickly deplete a computers RAM. Below we use `sim_survey` to simulate two surveys over a default population, of which one is set-up to have higher sampling effort than the other.

@@

Again, this function retains all the objects listed in the output of `sim_distribution` and adds data.tables that detail the set locations (`setdet`) and sampling details (`samp`). Catchability corrected abundance matrices, named `I` and `I_at_length`, are also produced and added to the output; these matrices are useful for comparing the true abundance available to the survey to abundance estimates obtained using design-based or model-based analyses of the simulated survey data. Specific surveys can be explored using the `plot_survey` function, which uses plotly [@sievert2018] and crosstalk [@cheng2016] in the background to link the bubble plot of aggregate set catch to the histogram of lengths and ages sampled to facilitate explorations of set-specific catches. The plots generated below have been combined here into a static plot for this paper (Figure \@ref(fig:survey)).

@@

```{r survey, fig.cap = "Bubble plots and histograms of set catches from a simulated stratified-random survey of the case study population under relatively a) high and b) low sampling effort. Histograms of length and age composition include the distribution caught and sampled overlaid with a line of the true distribution of length and ages available to the survey. Note that the first simulation of the survey in year 20 is depicted here. These plots are produced by `plot_survey` when supplied survey data simulated using `sim_survey`."}

@@

As noted above, the amount of RAM a user's computer has may limit the utility of the `sim_survey` function for running thousands of simulations of the same survey. The `sim_survey_parallel` function was therefore constructed to facilitate the running of thousands of simulations without running into RAM limitations. This function is set-up to run multiple `sim_survey` calls in parallel using the **`doParallel`** package [@weston2015] and, as such, multiple loops can be run using the `n_loops` argument and within each loop multiple simulations can be run (controlled using the `n_sims` argument). Total simulations will be the product of `n_loops` and `n_sims` arguments. If more than one core (`cores`) is specified, then the simulations will be run in parallel to speed up the process. Low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower. The optimum ratio of `n_sims` to `n_loops` will depend on the amount of RAM and number of cores the user's computer has. In any case, this function simplifies the process of running thousands of simulations of the same survey and the simulated data can then be supplied to survey-based or model-based analyses that require simulation testing.

@@

Once the survey data are simulated, they then need to be analyzed to obtain an index of abundance. While there are many model-based options for obtaining an index [e.g. @Thorson2015], survey-based approaches, such as stratified analyses, are often used. Here we apply formula presented in Smith and Somerton [-@Smith1981] to calculate stratified estimates of total abundance ($\hat{I}_{y,k}$), abundance at length ($\hat{I}_{l,y,k}$) and abundance at age ($\hat{I}_{a,y,k}$). Note that estimates of total abundance are based on aggregate catch while abundance at length requires length frequencies to be bumped up using set-specific ratios of measured to caught fish, and these length frequencies are converted to age by applying a division-level age-length-key. We used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance at age estimates from each survey:

>>>>

@@

Table: (\#tab:abundance) Default `sim_abundance` function call, with descriptions and associated parameter symbols of key arguments.

| **Function call**                           | **Description**                                            | **Symbol**                 |
|:------------------------------------------- |:---------------------------------------------------------- | :------------------------- |
| `sim_abundance(`                            | &nbsp;                                                     | &nbsp;                     |
| `+  ages = 1:20,`                           | Ages                                                       | $a$                        |
| `+  years = 1:20,`                          | Years                                                      | $y$                        |
| `+  R = sim_R(mean = 30000000,`             | Mean recruitment                                           | $\mu_r$                    |
| `+            log_sd = 0.5),`               | Standard deviation of log-recruitment                      | $\sigma_r$                 |
| `+  Z = sim_Z(mean = 0.5,`                  | Mean total mortality                                       | $\mu_Z$                    |
| `+            log_sd = 0.2,`                | Standard deviation of total mortality (log)                | $\sigma_Z$                 |
| `+            phi_age = 0.9,`               | Correlation across ages in error around total mortality    | $\varphi_{\delta, age}$    |
| `+            phi_year = 0.5),`             | Correlation across years in error around total mortality   | $\varphi_{\delta, year}$   |
| `+  growth = sim_vonB(Linf = 120,`          | Mean asymptotic length (cm)                                | $l_{\infty}$               |
| `+                    L0 = 5,`              | Length at birth (cm)                                       | $l_0$                      |
| `+                    K = 0.1,`             | Growth rate                                                | $K$                        |
| `+                    log_sd = 0.1,`        | Standard deviation of the von Bertalanffy growth curve     | $\sigma_l$                 |
| `+                    length_group = 3))`   | Length group bin size for abundance at length (cm)         | $l_{group}^{N}$            |

@@

Abundance is simulated using the `sim_abundance` function and a default function call is described in Table \@ref(tab:abundance). This function has a simple structure and requires the specification of a series of `ages` and `years` along with functions for simulating recruitment (`R`), total mortality (`Z`) and growth (`growth`). The package includes the functions `sim_R`, `sim_Z` and `sim_vonB` for simulating recruitment, total mortality and growth, respectively. These functions are "closures" [i.e. functions that contain data and return functions; @wickham2014] and this structure was chosen to avoid the repeated specifications of ages and years. The use of closures also allows users to use their own closures with a similar structure but different underlying formula. Overall, the function provides a simple tool for simulating a range dynamic age-structured populations. For instance, below we simulate a relatively long and short lived species (with default variance settings).

@@

The package also includes several plotting function for making quick plotly-based [@sievert2018] interactive visuals of the simulated population. For instance, the `plot_surface` function can be used to make quick visuals of matrices contained within the list returned by `sim_abundance`. As an example, we display the abundance at age matrix (object named `N` in the list produced by `sim_abundance`; Figure \@ref(fig:surface)); other names can be supplied to the `mat` argument to visualize a different matrix from the `sim_abundance` list, such as `Z`.

@@

```{r surface, fig.cap = "Surface plots of simulated abundance at age of a relatively a) long lived and b) short lived species. These plots were produced by `plot_surface` when supplied a list produced by `sim_abundance`."}

@@

The next step in the simulation is to distribute the abundance at age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ locations is generated with a resolution of $R$ and a depth gradient. The depth gradient is set-up to have a sigmoid shape with a depth range of $[d_{min}, d_{max}]$, shelf depth of $d_{shelf}$ and a shelf width of $w_{shelf}$. The grid is divided into $N_{div}$ divisions and $N_{strat}$ depth-based strata. The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean depth. This helps simulate depth preferences of particular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation within ages and years, and the two dimension AR1 age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations are controlled by a smoothing ($\lambda$) and a scaling parameter ($\kappa$) [here $\kappa$ is approximated from the range parameter ($r$), $\kappa = \sqrt{8 \lambda} / r$; @Blangiardo2015] and correlation across ages and years is controlled by $\varphi_{\xi, age}$ and $\varphi_{\xi, year}$, respectively. The overall variance of the process is controlled by $\sigma_{\xi}^2$. In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid. A more detailed description of the space-age-year covariance is included in Appendix 2.

Table: (\#tab:distribution) Default `sim_distribution` function call, with descriptions and associated parameter symbols of key arguments.

| **Function call**                                       | **Description**                                       | **Symbol**            |
|:------------------------------------------------------- |:----------------------------------------------------- | :-------------------- |
| `sim_distribution(`                                     | &nbsp;                                                | &nbsp;                |
| `+  sim,`                                               | Simulated population from `sim_abundance`             | &nbsp;                |
| `+  grid = make_grid(x_range = c(-140, 140),`           | Range of grid in the x dimension                      | &nbsp;                |
| `+                   y_range = c(-140, 140),`           | Range of grid in the y dimension                      | &nbsp;                |
| `+                   res = c(3.5, 3.5),`                | Grid resolution (km)                                  | $R$                   |
| `+                   shelf_depth = 200,`                | Shelf depth (km)                                      | $d_{shelf}$           |
| `+                   shelf_width = 100,`                | Shelf width (km)                                      | $w_{shelf}$           |
| `+                   depth_range = c(0, 1000),`         | Depth range (m)                                       | $[d_{min}, d_{max}]$  |
| `+                   n_div = 1,`                        | Number of divisions                                   | $N_{div}$             |
| `+                   strat_breaks = seq(0, 1000, 40)),` | Series of depth breaks for defining strata            | &nbsp;                |
| `+  ays_covar = sim_ays_covar(sd = 2.8,`                | Standard deviation of age-year-space distribution     | $\sigma_{\xi}$        |
| `+                            range = 300,`             | Range of spatial correlation (km)                     | $r$                   |
| `+                            lambda = 1,`              | Smoothness of spatial correlation                     | $\lambda$             |
| `+                            phi_age = 0.5,`           | Correlation across ages in spatial distribution       | $\varphi_{\xi, age}$  |
| `+                            phi_year = 0.9,`          | Correlation across years in spatial distribution      | $\varphi_{\xi, year}$ |
| `+                            group_ages = 5:20),`      | Make space-age-year variance equal across these ages  | &nbsp;                |
| `+  depth_par = sim_parabola(mu = 200,`                 | Depth at which abundance is typically highest (m)     | $\mu_d$               |
| `+                           sigma = 70))`              | Dispersion around depth of peak abundance (m)         | $\sigma_d$            |

@@

The `make_grid` function is used to generate a survey grid for use in the `sim_distribution` function. The output from `make_grid` is a raster object [@hijmans2016] with four layers: `depth`, `cell`, `division` and `strat`. If a more detailed and realistic grid is required, users can manually generate their own survey grid using real data and this grid can be supplied as a raster to `sim_distribution` if the same structure is used. The package includes a manually constructed survey grid of NAFO division 3Ps (named `survey_grid`) and the data-raw folder in the GitHub directory includes the data and code used to construct this grid. However, for simplicity, we use `make_grid` to construct a square grid for a default run of `sim_distribution`. Below we generate and plot (Figure \@ref(fig:grid)) a default grid, another grid with the number of strata increased by increasing the number of `strat_splits`, and another with four divisions and a more linear gradient in depth.

@@

a <- make_grid(n_div = 1, strat_splits = 2, shelf_depth = 200,
               shelf_width = 100, depth_range = c(0, 1000))
b <- make_grid(n_div = 1, strat_splits = 3, shelf_depth = 200, 
               shelf_width = 100, depth_range = c(0, 1000))
c <- make_grid(n_div = 4, strat_splits = 1, shelf_depth = 500, 
               shelf_width = 0, depth_range = c(0, 1000))
plot_grid(a)
plot_grid(b)
plot_grid(c)

@@

a <- make_grid() %>% 
  plot_grid(showscale = TRUE) %>% 
  add_labels(x = 0, y = 1, text = "a)")
b <- make_grid(strat_splits = 3) %>% 
  plot_grid(showscale = FALSE) %>% 
  add_labels(x = 0.04, y = 1, text = "b)")
c <- make_grid(n_div = 4, shelf_depth = 500, shelf_width = 0, depth_range = c(0, 1000)) %>% 
  plot_grid(showscale = FALSE) %>% 
  add_labels(x = 0.08, y = 1, text = "c)")
p <- subplot(a, b, c)

export_plot(p, file = "analysis/paper/figures/plot_grid.png", width = 800, height = 320)

@@

```{r grid, fig.cap = "Plots produced by `plot_grid` when supplied a raster object produced by `make_grid` a) using default settings, b) settings that increase the number of times depth strata are horizontally split, and c) settings that produce a more linear depth gradient and increase the number of divisions. In these plots, the color gradient represents depth, the thick grey lines delineate divisions and thin white lines delineate strata."}

@@

The `sim_distribution` function distributes the population simulated using `sim_abundance` throughout the grid generated using `make_grid`. Table \@ref(tab:distribution) outlines the default settings used for the function. In addition to supplying objects produced by `sim_abundance` and `make_grid`, this function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by tweaking a few parameters in these closures. Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider range) and exhibits stronger correlation across ages than years. Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years`, respectively, arguments in the `sim_ays_covar` closure. Variance in the size of the clusters can also be modified by changing the `sd` argument in the `sim_ays_covar` function. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fidelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the **`SimSurvey`** package have been set-up to be pipe [`%>%`; @bache2014] friendly.

@@

set.seed(438)
a <- sim_distribution(sim = sim_abundance(), # nested approach
                      ays_covar = sim_ays_covar(range = 300,
                                                phi_year = 0.9,
                                                phi_age = 0.5))
b <- sim_abundance() %>%  # pipe approach
  sim_distribution(ays_covar = sim_ays_covar(range = 2000,
                                             phi_year = 0.2,
                                             phi_age = 0.9))

@@

This function retains all the data simulated by `sim_abundance` and adds a data.table [@dowle2017], named `sp_N`, with abundance (`N`) split by `age`, `year` and `cell`. The function also retains the grid object and converts these data into a data.table, named `grid_xy`, with headers `x`, `y`, `depth`, `cell`, `division` and `strat`. The `sp_N` object can be merge with the `grid_xy` data by `cell` to associate abundance with specific locations, depth, divisions or strata. The `plot_distribution` function can be used to provide a quick visual of the distribution across ages and years. The code below will generate interactive plots with an Age-Year slider, however, for this paper we present a facet plot of the simulated data (Figure \@ref(fig:distribution)).

@@

```{r distribution, fig.cap = "Distribution plots of simulated populations that form a) tight clusters with stronger correlation through years than ages (default settings), and b) relatively diffuse clusters with stronger correlation through ages than years. This plot is a facet of plots produced by `plot_distribution` when supplied simulations from `sim_distribution`."}

@@

The final step in the simulation is to conduct a stratified random survey over the age-year-space array generated. The area of each strata is calculated and this is used to define the number of sets to allocate to each strata under a particular set density, $D_{sets}$. The allocated number of cells are randomly selected in each strata and the number of fish caught in each set is calculated by applying binomial sampling of the fish in each sampled cell by the proportion of the area covered by the trawl and the catchability of each age:

$$n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A_{trawl}}{A_{cell}} q_a )$$
Where $n_{a,y,s}$ is the number of fish sampled by a set, $A_{trawl}$ indicates the area covered by the trawl, $A_{cell}$ is the area of a grid cell, and $q_a$ is the catchability coefficient of each age. Here, catchabilities were defined using a logistic curve controlled by a steepness, $k$, and midpoint parameter, $x_0$. The lengths of the fish sampled by the set are then simulated using the von Bertalanffy growth equation found above in the [Simulate abundance] section. Depending on the number of fish caught, sub-sampling is then conducted. Specifically, a maximum number of lengths are measured per set, $M_{lengths}$, and a maximum number of ages, $M_{ages}$, are sampled per length group, $l_{group}$, per division. Such sub-sampling is common in fisheries-independent surveys as it is costly to sample every fish captured. Age determination is especially time-consuming, which is why age sampling tends to be length-stratified.

@@

| **Function call**                   | **Description**                                                         | **Symbol**     |
|:----------------------------------- |:----------------------------------------------------------------------- | :------------- |
| `sim_survey(`                       | &nbsp;                                                                  | &nbsp;         |
| `+  sim,`                           | Simulated spatial population from `sim_distribution`                    | &nbsp;         |
| `+  n_sims = 1`                     | Number of times to repeat the survey                                    | &nbsp;         |
| `+  q = sim_logistic(k = 2,`        | Steepness of logistic curve of catchability                             | $k$            |
| `+                   x0 = 3),`      | Midpoint of logistic curve of catchability                              | $x_0$          |
| `+  trawl_dim = c(1.5, 0.02),`      | Trawl dimensions (length, width; km) - i.e. area covered by a trawl     | $A_{trawl}$    |
| `+  min_sets = 2`                   | Minimum number of sets to conduct per strata                            | &nbsp;         |
| `+  set_den = 2/1000,`              | Set density (km^-2^)                                                    | $D_{sets}$     |
| `+  lengths_cap = 500,`             | Maximum number of lengths to collect / set                              | $M_{lengths}$  |
| `+  length_group = 1,`              | Length group bin size for age sampling (cm)                             | $l_{group}$    |
| `+  ages_cap = 10,`                 | Maximum number of ages to sample / length group / division              | $M_{ages}$     |
| `+  age_sammpling = "stratified")`  | Controls whether age sampling is length `"stratified"` or `"random"`    | &nbsp;         |

@@

The function `sim_survey` can be used to simulate data from one survey over a population created using `sim_distribution`. A default function call is described in Table \@ref(tab:survey)). The `sim_survey` function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Multiple simulations of the same survey can be run using the `n_sims` argument, however, requesting large numbers of simulations can be computational demanding depending on the processing capacity available. Below we use `sim_survey` to simulate two surveys over a default population, of which one is set-up to have higher sampling effort than the other.

@@

Again, this function retains all the objects listed in the output of `sim_distribution` and adds data.tables that detail the set locations (`setdet`) and sampling details (`samp`). Catchability corrected abundance matrices, named `I` and `I_at_length`, are also produced and added to the output; these matrices are useful for comparing the true abundance available to the survey to abundance estimates obtained using design-based or model-based analyses of the simulated survey data. Specific surveys can be explored using the `plot_survey` function, which uses plotly [@sievert2018] and crosstalk [@cheng2016] in the background to link the bubble plot of aggregate set catch to the histogram of lengths and ages sampled to facilitate explorations of set-specific catches (Figure \@ref(fig:survey)).

@@

```{r survey, fig.cap = "Bubble plots and histograms of set catches from a simulated stratified-random survey of a default population under relatively a) high and b) low sampling effort. Histograms of length and age composition include the distribution caught and sampled overlaid with a line of the true distribution of length and ages available to the survey. Note that the first simulation of the survey in year 20 is depicted here. These plots are produced by `plot_survey` when supplied survey data simulated using `sim_survey`."}

@@

As noted above, available RAM may limit the utility of the `sim_survey` function for running thousands of simulations of the same survey. The `sim_survey_parallel` function was therefore constructed to facilitate the running of thousands of simulations without running into RAM limitations. This function is set-up to run multiple `sim_survey` calls in parallel using the **`doParallel`** package [@weston2015] and, as such, multiple loops can be run using the `n_loops` argument and within each loop multiple simulations can be run (controlled using the `n_sims` argument). Total simulations will be the product of `n_loops` and `n_sims` arguments. If more than one core (`cores`) is specified, then the simulations will be run in parallel to speed up the process. Low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower. The optimum ratio of `n_sims` to `n_loops` will depend on the amount of RAM and number of cores the user's computer has. In any case, this function simplifies the process of running thousands of simulations of the same survey and the simulated data can then be supplied to survey-based or model-based analyses that require simulation testing.

@@

Once the survey data are simulated, they then need to be analyzed to obtain an index of abundance. While there are many model-based options for obtaining an index [e.g. @Thorson2015], survey-based approaches, such as stratified analyses, are often used. Here we apply formula presented in Smith and Somerton [-@Smith1981] to calculate stratified estimates of total abundance ($\hat{I}_{y,k}$), abundance at length ($\hat{I}_{l,y,k}$) and abundance at age ($\hat{I}_{a,y,k}$). Note that estimates of total abundance are based on aggregate catch while abundance at length requires length frequencies to be scaled up using set-specific ratios of measured to caught fish, and these length frequencies are converted to age by applying a division-level age-length-key. We used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance at age estimates from each survey:
